Title

### 2024-05-06 paper/main.tex
Updates

To perform any causal effect identification or estimation in Pearl's Directed
Acyclic Graphs (DAGs) based causal inference usually requires to come up with
the DAG structure. Learning these DAG structures from data is known as
\emph{causal discovery}. Plenty of algorithms have been developed for these in
the literature such as constraint-based methods such as PC, FCI, score based
methods such as Hill-Climb Search, GES, and constrained continuous optimization
based such as No TEARS.

@@

Even with the existence of all these algorithms for constructing DAGs from
data, in applied fields researchers prefer to construct DAGs by hand. We
hypothesize that the adaption of these algorithms in applied literature is
low due to the following reasons:
\begin{enumerate}
	\item Algorithms can make very obvious mistakes at times making it harder
		for the user to trust their outputs.
	\item Difficult to choose a single algorithm and their hyper-parameters.
\end{enumerate}

@@

When these models are constructed manually, it is extremely important that they
are tested before they are used for making any inference. Local testing methods
have been used for this purpose, where the implied conditional independences of
the model are testing in the data using statistical tests. These tests can then
be used to modify our models.

>>>>

\todo[inline]{Add citations}

To perform any causal effect identification or estimation in Pearl's Directed
Acyclic Graphs (DAGs) based causal framework usually requires to come up with
the DAG structure. Learning these DAG structures from data is known as
\emph{causal discovery}. Plenty of algorithms have been developed for these in
the literature such as constraint-based methods such as PC, FCI, score based
methods such as Hill-Climb Search, GES, and constrained continuous optimization
based such as No TEARS. All these algorithms take different approaches to
causal discovery, constraint-based algorithms utilize statistical conditional
independence (CI) tests to come up with a model structure, the score-based
methods iteratively perform local modifications to the model such that some
score function is maximized, the continuous optimization methods reformulate
the problem statement as a constrained optimization problem and use
optimization algorithms to come up with a graph.

@@

Even though we have various algorithms for doing casual discovery, yet
researchers in applied fields prefer to construct these DAGs manually based on
their domain knowledge. We hypothesize the following two reasons for low
adaption of these methods in applied sciences:

\begin{enumerate}
	\item Algorithms making obvious mistakes: These algorithms often 
		make very obvious mistakes, making it harder for the user
		to trust them.
	\item Difficulties in choosing an algorithm: For any given dataset, the
		user need to make a choice of the algorithm. Given that these
		algorithms work very differently, it can be difficult to make a
		choice. Additionally, each of these algorithms have
		hyperparameters and choices to make for them, making it
		difficult. As there is no way to evaluate the performance of 
		these algorithms on our dataset.
\end{enumerate}

@@

Both in the cases when the DAG is an output of an algorithm or when constructed
by hand, it is vital to test these models against data before using them for
making any inference. In the field of Structural Equation Models (SEMs)
modification indices have been used to do this. However, as modification index
is an evaluation of the global fit of the model. An alternative is local fit of
models using CI tests where the implied conditional independences of the model
can be tested using statistical tests. Similar to modification indices, these
tests can then be used to modify our models. Figure shows an example of this
testing.
